Diagnoses and cell types

### 2025-09-05 analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
Update analyses/infercnv-consensus-cell-type/exploratory-notebooks/reference-query-counts.Rmd
Co-authored-by: Joshua Shapiro <josh.shapiro@ccdatalab.org>

      celltype_groups <- diagnosis_celltype_map |>
        dplyr::filter(diagnosis_group == broad_diagnosis) |>
        tidyr::separate_rows(celltype_groups, sep = ",") |>
        dplyr::pull(celltype_groups)

>>>>

      celltype_groups <- diagnosis_celltype_map |>
        dplyr::filter(diagnosis_group == broad_diagnosis) |>
        tidyr::separate_rows(celltype_groups, sep = ",") |>
        dplyr::pull(celltype_groups) |>
        stringr::str_trim()
